Adaptive evolution with aneuploidy and mutation

### 2022-06-28 ms/ms.tex

% Fig dynamics
\begin{figure}[h!]
  \begin{subfigure}{\textwidth}
      \centering
      %% generated with dynamics-plot.ipynb
      \includegraphics[width=7in,height=2.5in]{../figures/full_dynamic_MAP.pdf}      
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/histo_100000.pdf}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/scatter100000_log_star.pdf}
  \end{subfigure}
  \caption{
    \textbf{Posterior genotype frequency dynamics.}     
    \textbf{(A)} Posterior predicted genotype frequencies over time, including the source of \eumt: $2n^*_A$ arose from $2n+1$, whereas $2n^*_M$ arose directly from $2n$. Shown are 50 simulations using the MAP estimate parameters.
    \textbf{(B)} Posterior distribution of $F_A$, the expected frequency of \eumt\ cells descended from \anwt\ cells, computed as the average frequency at the end of 100 simulations for 100,000 samples from the parameter posterior distribution.
    Solid and dashed lines show the mean and 95\% CI.
	\textbf{(C)} $F_A$ values (color coded) from panel B, with their corresponding mutation rate $\mu$ on x-axis and aneuploidy rate $\delta$ on the y-axis.
	White star shows the MAP estimate. See also \Cref{fig:posterior_FA_supp}.
     }
  \label{fig:ppc-plot}
\end{figure}

@@

% FIG posterior F_A supplementary
\begin{figure}[p]
	\begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/scatter100000_rater_fitr_from_wt.pdf}      
	\end{subfigure}
	  \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/scatter100000_rater_fitr_mut.pdf}
  \end{subfigure}
	\caption{\textbf{Posterior distribution of $F_A$.}
	\textbf{(A,B)} $F_A$ values (color coded) as in \Cref{fig:ppc-plot} for different parameter choices on the x- and y-axes. White star denotes the MAP estimate.
	}
    \label{fig:posterior_FA_supp}
\end{figure}

>>>>

% Fig dynamics
\begin{figure}[h!]
  \begin{subfigure}{\textwidth}
      \centering
      %% generated with dynamics-plot.ipynb
      \includegraphics[width=\textwidth]{../figures/MAP_freq_dynamics.pdf}      
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/F_A_posterior.pdf}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/F_A_mu_delta.pdf}
  \end{subfigure}
  \caption{
    \textbf{Posterior genotype frequency dynamics.}     
    \textbf{(A)} Posterior predicted genotype frequencies over time, including the source of \eumt: $2n^*_A$ arose from $2n+1$, whereas $2n^*_M$ arose directly from $2n$. Shown are 50 simulations using the MAP estimate parameters.
    \textbf{(B)} Posterior distribution of $F_A$, the expected frequency of \eumt\ cells descended from \anwt\ cells, computed as the average frequency at the end of 100 simulations for 100,000 samples from the parameter posterior distribution.
    Solid and dashed lines show the mean and 95\% CI.
	\textbf{(C)} $F_A$ values (color coded) from panel B, with their corresponding mutation rate $\mu$ on x-axis and aneuploidy rate $\delta$ on the y-axis.
	White star shows the MAP estimate. See also \Cref{fig:posterior_FA_supp}.
     }
  \label{fig:ppc-plot}
\end{figure}

@@

% FIG posterior F_A supplementary
\begin{figure}[p]
	\begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/F_A_delta-mu-ratio_1.pdf}      
	\end{subfigure}
	  \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/F_A_delta-mu-ratio_2.pdf}
  \end{subfigure}
	\caption{\textbf{Posterior distribution of $F_A$.}
	\textbf{(A,B)} $F_A$ values (color coded) as in \Cref{fig:ppc-plot} for different parameter choices on the x- and y-axes. White star denotes the MAP estimate.
	}
    \label{fig:posterior_FA_supp}
\end{figure}
